
---
title: What are differences between President from the South and North before civilwar?
output: html_notebook

---
In this project, we want to explore the difference between the president that is raised and born in the South(state with slavery) and North, Since after the civil war the cultural boundary between the North and South have been diminished. I just choose presidents from George Washington to Benjamin Harrison, the last president who has became adult before civil war,based on the assumptions that peoples ideology and characteristic are formed in their early adulthood so they should not be influenced by post-war situitions 


```{r, message=FALSE, warning=FALSE}
packages.used=c("rvest", "tibble", "qdap", 
                "sentimentr", "gplots", "dplyr",
                "tm", "syuzhet", "factoextra", 
                "beeswarm", "scales", "RColorBrewer",
                "RANN", "tm", "topicmodels")

# check packages that need to be installed.
packages.needed=setdiff(packages.used, 
                        intersect(installed.packages()[,1], 
                                  packages.used))
# install additional packages
if(length(packages.needed)>0){
  install.packages(packages.needed, dependencies = TRUE)
}

# load packages

library("rvest")
library("tibble")
library("qdap")
library("sentimentr")
library("gplots")
library("dplyr")
library("tm")
library("png")
library("syuzhet")
library("factoextra")
library("beeswarm")
library("scales")
library("RColorBrewer")
library("RANN")
library("tm")
library("topicmodels")
library("xlsx")
library("wordcloud")
library("tidytext")
source("../lib/plotstacked.R")
source("../lib/speechFuncs.R")
```
This notebook was prepared with the following environmental settings.

```{r}
print(R.version)
```
#Data Harvest
 we selected all inaugural addresses of past presidents, for lack of data of nominal and farewell addresses of president before civil war. 

```{r, message=FALSE, warning=FALSE}
### Inauguaral speeches
main.page <- read_html(x = "http://www.presidency.ucsb.edu/inaugurals.php")
# Get link URLs
# f.speechlinks is a function for extracting links from the list of speeches. 
inaug=f.speechlinks(main.page)
#head(inaug)
#as.Date(inaug[,1], format="%B %e, %Y")
inaug=inaug[-nrow(inaug),] # remove the last line, irrelevant due to error.

```

Using speech metadata posted on <http://www.presidency.ucsb.edu/>, We prepared xlsx data sets for the speeches we will scrap. 
```{r}
picture <- readPNG("map.png")
grid::grid.raster(picture)
#plot(picture)
```
This is the data I have processed. I just choose presidents from George Washington to Benjamin Harrison, the last president who has became adult before civil war, based on the assumptions that peoples ideology and characteristic are formed in their early adulthood so they should not be influenced by post-war new ideology and impacts.

About one-third presidents were born and raised in the South, while the others were raised in the North part of America. We use the common Mason–Dixon line to seperate south and north as most people do. In the South, most Presidents are from Virginia and Tennessee,  in the North there are Presidents from New England, New York , iIlinois etc

```{r}

inaug.list = read.xlsx("../data/inauglist_place.xlsx", sheetIndex = 1)
```

We assemble all scrapped speeches into one list. Note here that we dont have the full text yet, only the links to full text transcripts. 
scrap the texts of speeches from the speech URLs.

```{r}
inaug.list$type=c(rep("inaug", nrow(inaug.list)))
inaug.list=cbind(inaug.list,inaug)
```

Based on the list of speeches, we scrap the main text part of the transcript's html page. For simple html pages of this kind. For reproducibility, we also save our scrapped speeches into our local folder as individual speech files. 

Now we combine the information from the internet and dataset, combine the columns of important data frame to generate further useful information, first combine the html and data and then download scripts to local repository.

```{r}
# Loop over each row in speech.list
inaug.list$fulltext=NA
for(i in seq(nrow(inaug.list))) {
  text <- read_html(inaug.list$urls[i]) %>% # load the page
    html_nodes(".displaytext") %>% # isloate the text
    html_text() # get the text
inaug.list$fulltext[i]=text

  # Create the file name
 #filename <- paste0("../data/inaugurals/", 
#if(inaug.list$File[i]%in% nouu)#levels(sentencep.list.place$File))
#{
  filename <- paste0("../data/inaugurals/", 
                     inaug.list$type[i],
                     inaug.list$File[i], "-", 
                     inaug.list$Term[i], ".txt")
  sink(file = filename) %>% # open file to write 
    cat(text)  # write the file
  sink() # close the file
#}
}
```

We will use sentences as units of analysis for this project, as sentences are natural languge units for organizing thoughts and ideas. For each extracted sentence, we apply sentiment analysis using NRC sentiment. "The NRC Emotion Lexicon is a list of English words and their associations with eight basic emotions (anger, fear, anticipation, trust, surprise, sadness, joy, and disgust) and two sentiments (negative and positive). The annotations were manually done by crowdsourcing."

We assign an sequential id to each sentence in a speech (`sent.id`) and also calculated the number of words in each sentence as *sentence length* (`word.count`).

```{r, message=FALSE, warning=FALSE}
sentence.list=NULL

for(i in 1:nrow(inaug.list)){
  sentences=sent_detect(inaug.list$fulltext[i],
                        endmarks = c("?", ".", "!", "|",";"))
  if(length(sentences)>0){
    emotions=get_nrc_sentiment(sentences)
    word.count=word_count(sentences)
    # colnames(emotions)=paste0("emo.", colnames(emotions))
    # in case the word counts are zeros?
    emotions=diag(1/(word.count+0.01))%*%as.matrix(emotions)
    sentence.list=rbind(sentence.list, 
                        cbind(inaug.list[i,-ncol(inaug.list)],
                              sentences=as.character(sentences), 
                              word.count,
                              emotions,
                              sent.id=1:length(sentences)
                        )
    )
  }
}
```

Some non-sentences exist in raw data due to erroneous extra end-of-sentence marks. And we also delete presidents that do not belong to our Category.
```{r}
sentence.list=sentence.list%>%filter(!is.na(word.count)) 

sentence.list.place<-sentence.list[as.logical(1-is.na(sentence.list$Places)),]
```

Data analysis --- length of sentences

For simpler visualization, we chose a subset of better known presidents or presidential candidates on which to focus our analysis. 
Let us haveOverview of sentence length distribution by different types of speeches. let us see how presidents inaugural length from different regions differ

inaugural speeches 


```{r, fig.width = 3, fig.height = 3}

par(mar=c(4, 11, 2, 2))


sentence.list.place$File=factor(sentence.list.place$File)

sentence.list.place$FileOrdered=reorder(sentence.list.place$File, 
                                      sentence.list.place$word.count, 
                                      mean, 
                                      order=T)


# this is for each president
sentence.list.place$Filedirection=paste(sentence.list.place$FileOrdered,sentence.list.place$Places)
beeswarm(word.count~Filedirection, 
         data=sentence.list.place,
         horizontal = TRUE, 
         pch=16, 
         col=alpha(brewer.pal(9, "Set1"), 0.6), 
         cex=0.55, cex.axis=0.8, cex.lab=0.8,
         spacing=5/nlevels(sentence.list.place$FileOrdered),
         las=2, xlab="Number of words in a sentence.", ylab="",
         main="Inaugural speeches")

# this is for overall places
beeswarm(word.count~Places,
         data=sentence.list.place,
         horizontal = TRUE, 
         pch=16, 
         col=alpha(brewer.pal(9, "Set1"), 0.6), 
         cex=0.55, cex.axis=0.8, cex.lab=0.8,
         spacing=5/nlevels(sentence.list.place$FileOrdered),
         las=2, xlab="Number of words in a sentence.", ylab="",
         main="Inaugural speeches")

```



And we want explore the short sentences presidents usually say:
```{r}
#president from South
sentence.list.place%>%
  filter(File=="GeorgeWashington",word.count<=10)%>%
  select(sentences)#%>%sample_n(10)


sentence.list.place%>%
  filter(File=="JohnAdams", 
         word.count<=10)%>%
  select(sentences)

sentence.list.place%>%
  filter(File=="AbrahamLincoln", 
         word.count<=10)%>%
  select(sentences)#%>%sample_n(10)


#
folder.path="../data/inaugurals/"
ff.all<-Corpus(DirSource(folder.path))
ff.all<-tm_map(ff.all, stripWhitespace)
ff.all<-tm_map(ff.all, content_transformer(tolower))
ff.all<-tm_map(ff.all, removeWords, stopwords("english"))
ff.all<-tm_map(ff.all, removeWords, character(0))
ff.all<-tm_map(ff.all, removePunctuation)
tdm.all<-TermDocumentMatrix(ff.all)
tdm.tidy=tidy(tdm.all)
tdm.overall=summarise(group_by(tdm.tidy, term), sum(count))
wordcloud(tdm.overall$term, tdm.overall$`sum(count)`,
          scale=c(5,0.5),
          max.words=100,
          min.freq=1,
          random.order=FALSE,
          rot.per=0.3,
          use.r.layout=T,
          random.color=FALSE,
          #colors="BLUE"))
          colors=brewer.pal(9,"Blues"))

# the 
folder.path1="../data/inaugurals/beforewar/"
ff.beforewar<-Corpus(DirSource(folder.path1))
ff.beforewar<-tm_map(ff.beforewar, stripWhitespace)
ff.beforewar<-tm_map(ff.beforewar, content_transformer(tolower))
ff.beforewar<-tm_map(ff.beforewar, removeWords, stopwords("english"))
ff.beforewar<-tm_map(ff.beforewar, removeWords, character(0))
ff.beforewar<-tm_map(ff.beforewar, removePunctuation)
tdm.allbef<-TermDocumentMatrix(ff.beforewar)
tdm.tidybef=tidy(tdm.allbef)
tdm.overallb=summarise(group_by(tdm.tidybef, term), sum(count))
wordcloud(tdm.overallb$term, tdm.overallb$`sum(count)`,
          scale=c(5,0.5),
          max.words=100,
          min.freq=1,
          random.order=FALSE,
          rot.per=0.3,
          use.r.layout=T,
          random.color=FALSE,
          #colors="BLUE"))
          colors=brewer.pal(9,"Greens"))

folder.pathn="../data/inaugurals/beforewar/north"
ff.alln<-Corpus(DirSource(folder.pathn))
ff.alln<-tm_map(ff.alln, stripWhitespace)
ff.alln<-tm_map(ff.alln, content_transformer(tolower))
ff.alln<-tm_map(ff.alln, removeWords, stopwords("english"))
ff.alln<-tm_map(ff.alln, removeWords, character(0))
ff.alln<-tm_map(ff.alln, removePunctuation)
tdm.alln<-TermDocumentMatrix(ff.alln)
tdm.tidyn=tidy(tdm.alln)
tdm.overalln=summarise(group_by(tdm.tidyn, term), sum(count))
wordcloud(tdm.overalln$term,tdm.overalln$`sum(count)`,
          scale=c(5,0.5),
          max.words=100,
          min.freq=1,
          random.order=FALSE,
          rot.per=0.3,
          use.r.layout=T,
          random.color=FALSE,
          #colors="BLUE"))
          colors=brewer.pal(9,"Reds"))

folder.paths="../data/inaugurals/beforewar/south"
ff.alls<-Corpus(DirSource(folder.paths))
ff.alls<-tm_map(ff.alls, stripWhitespace)
ff.alls<-tm_map(ff.alls, content_transformer(tolower))
ff.alls<-tm_map(ff.alls, removeWords, stopwords("english"))
ff.alls<-tm_map(ff.alls, removeWords, character(0))
ff.alls<-tm_map(ff.alls, removePunctuation)
tdm.alls<-TermDocumentMatrix(ff.alls)
tdm.tidys=tidy(tdm.alls)
tdm.overalls=summarise(group_by(tdm.tidys, term), sum(count))
wordcloud(tdm.overalls$term, tdm.overalls$`sum(count)`,
          scale=c(5,0.5),
          max.words=100,
          min.freq=1,
          random.order=FALSE,
          rot.per=0.3,
          use.r.layout=T,
          random.color=FALSE,
          #colors="BLUE"))
          colors=brewer.pal(9,"Blues"))
```




#Data analysis 

Sentence length variation over the course of the speech, with emotions. 

How our presidents (or candidates) alternate between long and short sentences and how they shift between different sentiments in their speeches. It is interesting to note that some presidential candidates' speech are more colorful than others. 


```{r, fig.height=2.5, fig.width=2}
par(mfrow=c(4,1), mar=c(1,0,2,0), bty="n", xaxt="n", yaxt="n", font.main=1)

f.plotsent.len(In.list=sentence.list, InFile="GeorgeWashington", 
InType="inaug", InTerm=1, President="George Washington")

f.plotsent.len(In.list=sentence.list, InFile="ThomasJefferson", 
InType="inaug", InTerm=1, President="Thomas Jefferson")

f.plotsent.len(In.list=sentence.list, InFile="AbrahamLincoln", 
InType="inaug", InTerm=1, President="Abraham Lincoln")

f.plotsent.len(In.list=sentence.list, InFile="RutherfordBHayes", 
InType="inaug", InTerm=1, President="Rutherford B. Hayes")
```

#Then I am going to find some sentences that can have a good represent of the president's characteristic

```{r}
cat("\nGeorge Washingto\n")
speech.df=tbl_df(sentence.list.place)%>%
filter(File=="GeorgeWashington", type=="inaug", word.count>=4)%>%
select(sentences, anger:trust)
speech.df=as.data.frame(speech.df)
as.character(speech.df$sentences[apply(speech.df[,-1], 2, which.max)])

cat("\nThomas Jefferson\n")
speech.df=tbl_df(sentence.list.place)%>%
filter(File=="ThomasJefferson", type=="inaug", Term==1, word.count>=5)%>%
select(sentences, anger:trust)
speech.df=as.data.frame(speech.df)
as.character(speech.df$sentences[apply(speech.df[,-1], 2, which.max)])

cat("\nAbraham Lincoln\n")
speech.df=tbl_df(sentence.list.place)%>%
filter(File=="AbrahamLincoln", type=="inaug", Term==1, word.count>=4)%>%
select(sentences, anger:trust)
speech.df=as.data.frame(speech.df)
as.character(speech.df$sentences[apply(speech.df[,-1], 2, which.max)])

cat("\nRutherford B. Hayes\n")
speech.df=tbl_df(sentence.list.place)%>%
filter(File=="RutherfordBHayes", type=="inaug", Term==1, word.count>=5)%>%
select(sentences, anger:trust)
speech.df=as.data.frame(speech.df)
as.character(speech.df$sentences[apply(speech.df[,-1], 2, which.max)])

```


# Clustering of emotions
```{r, fig.width=2, fig.height=2}
heatmap.2(cor(sentence.list%>%filter(type=="inaug")%>%select(anger:trust)), 
scale = "none", 
col = bluered(100), , margin=c(6, 6), key=F,
trace = "none", density.info = "none")

par(mar=c(4, 6, 2, 1))
emo.means.north=colMeans(select(sentence.list.place%>%filter(Places=="N"), anger:trust)>0.01)
emo.means.south=colMeans(select(sentence.list.place%>%filter(Places=="S"), anger:trust)>0.01)
col.use=c("red2", "darkgoldenrod1", 
"chartreuse3", "blueviolet",
"darkgoldenrod2", "dodgerblue3", 
"darkgoldenrod1", "darkgoldenrod1")
par(mfrow=c(1,2))
barplot(emo.means.north[order(emo.means.north)], las=2, col=col.use[order(emo.means.north)], horiz=T, main="North likely")
barplot(emo.means.south[order(emo.means.south)], las=2, col=col.use[order(emo.means.south)], horiz=T, main="South likely")
```

```{r, fig.height=3.3, fig.width=3.7}
presid.summary=tbl_df(sentence.list.place)%>%
filter(type=="inaug",)%>%
#group_by(paste0(type, File))%>%
group_by(Filedirection)%>%
summarise(
anger=mean(anger),
anticipation=mean(anticipation),
disgust=mean(disgust),
fear=mean(fear),
joy=mean(joy),
sadness=mean(sadness),
surprise=mean(surprise),
trust=mean(trust)
#negative=mean(negative),
#positive=mean(positive)
)

presid.summary=as.data.frame(presid.summary)
rownames(presid.summary)=as.character((presid.summary[,1]))
km.res=kmeans(presid.summary[,-1], iter.max=200,
5)
fviz_cluster(km.res, 
stand=F, repel= TRUE,
data = presid.summary[,-1], xlab="", xaxt="n",
show.clust.cent=FALSE)
```

#LDA Data analysis 

For topic modeling, we prepare a corpus of sentence snipets as follows. For each speech, we start with sentences and prepare a snipet with a given sentence with the flanking sentences. 

```{r}
sentence.list<-sentence.list.place
corpus.list=sentence.list[2:(nrow(sentence.list)-1), ]
sentence.pre=sentence.list$sentences[1:(nrow(sentence.list)-2)]
sentence.post=sentence.list$sentences[3:(nrow(sentence.list)-1)]
corpus.list$snipets=paste(sentence.pre, corpus.list$sentences, sentence.post, sep=" ")
rm.rows=(1:nrow(corpus.list))[corpus.list$sent.id==1]
rm.rows=c(rm.rows, rm.rows-1)
corpus.list=corpus.list[-rm.rows, ]
```

## Text mining
```{r}
docs <- Corpus(VectorSource(corpus.list$snipets))
writeLines(as.character(docs[[sample(1:nrow(corpus.list), 1)]]))
```



```{r}
#remove potentially problematic symbols
docs <-tm_map(docs,content_transformer(tolower))
writeLines(as.character(docs[[sample(1:nrow(corpus.list), 1)]]))

#remove punctuation
docs <- tm_map(docs, removePunctuation)
writeLines(as.character(docs[[sample(1:nrow(corpus.list), 1)]]))

#Strip digits
docs <- tm_map(docs, removeNumbers)
writeLines(as.character(docs[[sample(1:nrow(corpus.list), 1)]]))

#remove stopwords
docs <- tm_map(docs, removeWords, stopwords("english"))
writeLines(as.character(docs[[sample(1:nrow(corpus.list), 1)]]))

#remove whitespace
docs <- tm_map(docs, stripWhitespace)
writeLines(as.character(docs[[sample(1:nrow(corpus.list), 1)]]))

#Stem document
docs <- tm_map(docs,stemDocument)
writeLines(as.character(docs[[sample(1:nrow(corpus.list), 1)]]))
```

#Topic modeling

Gengerate document-term matrices. 

```{r}
dtm <- DocumentTermMatrix(docs)
#convert rownames to filenames#convert rownames to filenames
rownames(dtm) <- paste(corpus.list$type, corpus.list$File,
corpus.list$Term, corpus.list$sent.id, sep="_")

rowTotals <- apply(dtm , 1, sum) #Find the sum of words in each Document

dtm  <- dtm[rowTotals> 0, ]
corpus.list=corpus.list[rowTotals>0, ]

```

Run LDA

```{r}
#Set parameters for Gibbs sampling
burnin <- 4000
iter <- 2000
thin <- 500
seed <-list(2003,5,63,100001,765)
nstart <- 5
best <- TRUE

#Number of topics
k <- 15

#Run LDA using Gibbs sampling
ldaOut <-LDA(dtm, k, method="Gibbs", control=list(nstart=nstart, seed = seed, best=best,burnin = burnin, iter = iter, thin=thin))
#write out results
#docs to topics
ldaOut.topics <- as.matrix(topics(ldaOut))
table(c(1:k, ldaOut.topics))
write.csv(ldaOut.topics,
          file=paste("../out/LDAGibbs",k,"DocsToTopics.csv"))

#top 6 terms in each topic
ldaOut.terms <- as.matrix(terms(ldaOut,20))
write.csv(ldaOut.terms,
          file=paste("../out/LDAGibbs",k,"TopicsToTerms.csv"))

#probabilities associated with each topic assignment
topicProbabilities <- as.data.frame(ldaOut@gamma)
write.csv(topicProbabilities,file=paste("/Users/westspringamerica/Downloads/wk2-TextMining/out/LDAGibbs",k,"TopicProbabilities.csv"))
```

```{r}
terms.beta=ldaOut@beta
terms.beta=scale(terms.beta)
topics.terms=NULL
for(i in 1:k){
topics.terms=rbind(topics.terms, ldaOut@terms[order(terms.beta[i,], decreasing = TRUE)[1:7]])
}
topics.terms
ldaOut.terms
```

Based on the most popular terms and the most salient terms for each topic, we assign a hashtag to each topic. This part require manual setup as the topics are likely to change. 

```{r}

topics.oldhash=c("Economy", "America", "Defense", "Belief", "Election", "Patriotism", "Unity", "Government", "Reform", "Temporal", "WorkingFamilies", "Freedom", "Equality", "Misc", "Legislation")

topicsnew.hash=c("everi", "war" ,"law",  "upon","nation", "union", "constitut","will","public","interest","state",     "great","duti", "peopl","right")
topics.hash=topicsnew.hash
corpus.list$ldatopic=as.vector(ldaOut.topics)
corpus.list$ldahash=topics.hash[ldaOut.topics]

colnames(topicProbabilities)=topics.hash
corpus.list.df=cbind(corpus.list, topicProbabilities)
```

# Clustering of topics
```{r, fig.width=3, fig.height=4}
par(mar=c(1,1,1,1))
topic.summary=tbl_df(corpus.list.df)%>%
filter(type%in%c("inaug"))%>%
select(Filedirection, everi: right)%>%
group_by(Filedirection)%>%
summarise_each(funs(mean))
topic.summary=as.data.frame(topic.summary)
rownames(topic.summary)=topic.summary[,1]


topic.plot=c(1:15)
print(topics.hash[topic.plot])

heatmap.2(as.matrix(topic.summary[,topic.plot+1]), 
scale = "column", key=F, 
col = bluered(100),
cexRow = 0.8, cexCol = 0.9, margins = c(8, 8),
trace = "none", density.info = "none")
```

```{r, fig.width=3.3, fig.height=5}
    


par(mfrow=c(5, 1), mar=c(1,1,2,0), bty="n", xaxt="n", yaxt="n")

topic.plot=c(1, 13, 14, 15, 8, 9, 12)
print(topics.hash[topic.plot])

speech.df=tbl_df(corpus.list.df)%>%filter(File=="GeorgeWashington", type=="inaug",Term==1)%>%select(sent.id, everi: right)
speech.df=as.matrix(speech.df)
speech.df[,-1]=replace(speech.df[,-1], speech.df[,-1]<1/15, 0.001)
speech.df[,-1]=f.smooth.topic(x=speech.df[,1], y=speech.df[,-1])
plot.stacked(speech.df[,1], speech.df[,topic.plot+1], 
xlab="Sentences", ylab="Topic share", main="GeorgeWashington")

speech.df=tbl_df(corpus.list.df)%>%filter(File=="ThomasJefferson", type=="inaug", Term==1)%>%select(sent.id, everi: right)
speech.df=as.matrix(speech.df)
speech.df[,-1]=replace(speech.df[,-1], speech.df[,-1]<1/15, 0.001)
speech.df[,-1]=f.smooth.topic(x=speech.df[,1], y=speech.df[,-1])
plot.stacked(speech.df[,1], speech.df[,topic.plot+1],
xlab="Sentences", ylab="Topic share", main="ThomasJefferson")

speech.df=tbl_df(corpus.list.df)%>%filter(File=="UlyssesSGrant", type=="inaug", Term==1)%>%select(sent.id, everi: right)
speech.df=as.matrix(speech.df)
speech.df[,-1]=replace(speech.df[,-1], speech.df[,-1]<1/15, 0.001)
speech.df[,-1]=f.smooth.topic(x=speech.df[,1], y=speech.df[,-1])
plot.stacked(speech.df[,1], speech.df[,topic.plot+1], 
xlab="Sentences", ylab="Topic share", main="UlyssesSGrant")

speech.df=tbl_df(corpus.list.df)%>%filter(File=="AbrahamLincoln", type=="inaug", Term==1)%>%select(sent.id, everi: right)
speech.df=as.matrix(speech.df)
speech.df[,-1]=replace(speech.df[,-1], speech.df[,-1]<1/15, 0.001)
speech.df[,-1]=f.smooth.topic(x=speech.df[,1], y=speech.df[,-1])
plot.stacked(speech.df[,1], speech.df[,topic.plot+1],
xlab="Sentences", ylab="Topic share", main="AbrahamLincoln")

speech.df=tbl_df(corpus.list.df)%>%filter(File=="JamesMonroe", type=="inaug",Term==1)%>%select(sent.id, everi: right)
speech.df=as.matrix(speech.df)
speech.df[,-1]=replace(speech.df[,-1], speech.df[,-1]<1/15, 0.001)
speech.df[,-1]=f.smooth.topic(x=speech.df[,1], y=speech.df[,-1])
plot.stacked(speech.df[,1], speech.df[,topic.plot+1],
xlab="Sentences", ylab="Topic share", main="JamesMonroe")

```


```{r, fig.width=3, fig.height=3}
presid.summary=tbl_df(corpus.list.df)%>%
filter(type=="inaug")%>%
select(Filedirection, everi: right)%>%
group_by(Filedirection)%>%
summarise_each(funs(mean))

presid.summary=as.data.frame(presid.summary)
rownames(presid.summary)=as.character((presid.summary[,1]))
km.res=kmeans(scale(presid.summary[,-1]), iter.max=200,
5)
fviz_cluster(km.res, 
stand=T, repel= TRUE,
data = presid.summary[,-1],
show.clust.cent=FALSE)
```
##Conclusions:
#According to the analysis, we find that
 When it comes to number of words in presidents'augural presentation, the south is not statistically different from the north, while they do speak a little shorter on average.


 All presidents like to use the word "WIll",maybe they are promising the audience with a good future or they would like to show his strong willingness. In early period "People" and "Government" has more chance to appear in the presentation than nowadays. Presidents from north like to say about "People", while "South" is more likely to talk about States. This really make sense that Southerners want a more united States instead of a United States with a strong government. And the north people urge them to liberate people of colored races.

 When evaluating emotions and length of Presidents,President lincoln's passage are very colorful of rhythm and emotions, we know he is very good at giving speech. As a whole, northern presidents has more fear and sad feelings then the south,while the south are more joyful and likely to surpise, this may to due to coldness of the north making people sorrow while the south has more sunny weathers. the cluster is not good enough to give the overview of all presidents because each president has his own unique features

 By topic modelling we find that the old topic are quite different from newer ones.and the heatmap are more clear to show there are southern and northern presidents seem to have some inner cores ,they may the same ancient synonym ancestry. and we also find the topics they are talking about are quite the same but not in the same form
